An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-16 draft.tex
KafkEO image

\section{State of the Art} 
\label{soa}

>>>>

\section{State of the Art} 
\label{soa}
Hadoop 
    Comparasion \cite{ferrucci2018using}
    Hadoop\cite{fazenda2012} 
    FlexGP \cite{FlexGP}, 
    elephant56 \cite{salza2016elephant56},

Pool
    SofEA \cite{merelo2012sofea,sofea:cec2012} , 
    EvoSpace \cite{garcia2015evospace},
Volunteer
    evospace-js \cite{garcia2017evospace}
Queue
    Containers \cite{valenzuela2015implementing} \cite{salza2016approach} 
    Seamless local and Cloud \cite{leclerc2016seamless}
    Serverless KafKEO \cite{guervos2018introducing}, 
    Docker Orchestation \cite{dziurzanski2020scalable,zhao2019cloud}
PSO 
    PSO AWS \cite{li2015parallel}
